### 2023-03-17 notebooks/conformal.qmd
more on sampling

opt = Descent(0.01)
ordered_names = [
    "Generic (γ=0.5)",
    "Generic (γ=0.9)",
    "Conformal (λ₂=1)",
    "Conformal (λ₂=10)"
]
loss_fun = Objectives.logitbinarycrossentropy

# Generators:
generators = Dict(
    ordered_names[1] => GenericGenerator(opt = opt, decision_threshold=0.5),
    ordered_names[2] => GenericGenerator(opt = opt, decision_threshold=0.9),
    ordered_names[3] => CCE.ConformalGenerator(loss=loss_fun, opt=opt, λ=[0.1,1]),
    ordered_names[4] => CCE.ConformalGenerator(loss=loss_fun, opt=opt, λ=[0.1,10]),
)

>>>>

opt = Descent(0.01)
ordered_names = [
    "Generic (γ=0.5)",
    "Conformal (λ₂=1)",
    "Conformal (λ₂=10)"
]
loss_fun = Objectives.logitbinarycrossentropy
generator = GenericGenerator(opt = opt)

# Generators:
generators = Dict(
    ordered_names[1] => generator,
    ordered_names[2] => deepcopy(generator) |> gen -> @objective(gen, _ + 0.1distance_l2 + 1.0set_size_penalty),
    ordered_names[3] => deepcopy(generator) |> gen -> @objective(gen, _ + 0.1distance_l2 + 10.0set_size_penalty),
)

counterfactuals = Dict([name => generate_counterfactual(x, target, counterfactual_data, M, gen; initialization=:identity, converge_when=:generator_conditions, gradient_tol=1e-3) for (name, gen) in generators])
